Distributed Version Control Systems

### 2010-04-27 paper.tex
Corregida una frase en la introducción de Architecture
Modificada la introducción de More Atomical Commits para que quede más en ingles :)

In a DVCS like Git, everybody has the full repository in their hard drives.
Since there is no central server, operations on the repository all are done 
offline. This means that actions like commiting do not depend on having a 
network connection, since commits are made on your repository.

@@

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes. 
Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).

>>>>

In a DVCS like Git, everybody has the full repository in their hard drives.
Since there is no central server, all the operations on the repository are done 
offline. This means that actions like commiting do not depend on having a 
network connection, since commits are made on your repository.

@@

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
is different, since commits are made in the local repository only. Therefore, they can be more atomic, 
because commits aren't huge changesets but can be logical, coherent and smaller changes.

Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).
